---
title: "Try3_with_RF_Plus_stepAIC__Plus_strat"
author: "Linxiao Bai"
date: "2/7/2017"
output: html_document
---
###Loading Packages and Data
```{r results='hide', message=FALSE, warning=FALSE}
library(MASS)
library(nnet)
library(randomForest)
library(leaps)
library(plyr)
library(e1071)
library(caret)
library(splitstackshape)
#please install all
#please change this directory
load('/Users/Pagliacci/Desktop/DSC450/samsungData.rda')
```
###Changing Column Names and Response Data Type to Vector
```{r}
colnames(samsungData) = make.names(names(samsungData), unique = TRUE)
samsungData$activity=as.factor(samsungData$activity)
```
###Some Basic Statisctics
```{r}
count(samsungData$activity)
```
###Resampling Data with stratifed, with respect to subject. 7:3 train test ratio.
```{r}
set.seed(1)
test= stratified(samsungData, c("subject"), 0.3)
train= samsungData[-as.numeric(rownames(test)),]
```
###Rough Selection with RF, Yield 50 variables, 
#####This step takes about 1mins
```{r}
n=50
model_RF_full = randomForest(activity~., data=train)
imp=varImp(model_RF_full)
imp$na=NA
feat=rownames(imp[order(-imp$Overall),])[1:n]
fml_RF_50=formula(paste("activity~",paste(feat,collapse="+")))
```

###Test Performance of Top50 Features on Test Data
```{r}
model_RF_50=randomForest(fml_RF_50,data=train)
mean(predict(model_RF_50,newdata=test)==test$activity)
```
###Construct Multinomial Logistic Regression Model with 50 Features
### and Test Accuracy on Test Data
```{r}
model_MM_50=multinom(fml_RF_50, data=train,trace=0)
mean(predict(model_MM_50,newdata=test)==test$activity)
```

###Forward Selection with AIC out of 50 Features
#####This step takes looooong, about several mins. Get coffee.
```{r}
step_result=stepAIC(multinom(activity~1,
                 data=train,trace=0),scope=fml_RF_50,direction='forward')
newfeat=attr(terms(step_result), "term.labels")

fml_step_2=formula(paste("activity~",paste(newfeat[1:2],collapse="+")))
fml_step_3=formula(paste("activity~",paste(newfeat[1:3],collapse="+")))


fml_step_2
fml_step_3
```
###Test Performance of New Features on Test Data with RF
```{r}
model_RF_2=randomForest(fml_step_2,data=train)
model_RF_3=randomForest(fml_step_3,data=train)

mean(predict(model_RF_2,newdata=test)==test$activity)
mean(predict(model_RF_3,newdata=test)==test$activity)
```
With two variables we achieve above 80% accuracy, and above 90% with three. Congrats!

